Identification Paper

### 2023-09-02 my_paper/tables/tab16-iat_regression_tab_byparent_type_county.tex
first commit

\caption{Hispanic identity and Skin Tone Implicit Bias Among Second Generation Hispanic Immigrants: By Parental Type  (MSA)\label{regtab-byparent-02}}
\centering
\resizebox{\linewidth}{!}{
\begin{tabular}[t]{lcccc}
\toprule
\multicolumn{1}{c}{ } & \multicolumn{1}{c}{All} & \multicolumn{1}{c}{HH} & \multicolumn{1}{c}{HW} & \multicolumn{1}{c}{WH} \\
\cmidrule(l{3pt}r{3pt}){2-2} \cmidrule(l{3pt}r{3pt}){3-3} \cmidrule(l{3pt}r{3pt}){4-4} \cmidrule(l{3pt}r{3pt}){5-5}
  & \specialcell{(1) \\ $H^2$} & \specialcell{(2) \\ $H^2$} & \specialcell{(3) \\ $H^2$} & \specialcell{(4) \\ $H^2$}\\
\midrule
Implicit Skin Tone Bias & \num{0.02} & \num{0.01} & \num{0.02} & \num{0.03}\\
 & (\num{0.01}) & (\num{0.01}) & (\num{0.03}) & (\num{0.04})\\
Female & \num{0.00} & \num{0.00}* & \num{-0.01} & \num{0.02}*\\
 & (\num{0.00}) & (\num{0.00}) & (\num{0.01}) & (\num{0.01})\\
College Graduate: Mother & \num{-0.05}*** & \num{-0.03}*** & \num{-0.06}*** & \num{-0.06}***\\
 & (\num{0.01}) & (\num{0.01}) & (\num{0.01}) & (\num{0.02})\\
College Graduate: Father & \num{-0.08}*** & \num{-0.04}*** & \num{-0.10}*** & \num{-0.11}***\\
 & (\num{0.01}) & (\num{0.01}) & (\num{0.02}) & (\num{0.01})\\
\midrule
N & \num{448014} & \num{327525} & \num{67837} & \num{52652}\\
Mean & \num{0.94} & \num{0.96} & \num{0.9} & \num{0.84}\\
Year-State FE & X & X & X & X\\
\bottomrule
\multicolumn{5}{l}{\rule{0pt}{1em}\textsuperscript{1} I include controls for sex, quartic age, parental education.}\\
\multicolumn{5}{l}{\rule{0pt}{1em}\textsuperscript{2} Standard errors are clustered on the state level}\\
\multicolumn{5}{l}{\rule{0pt}{1em}* p $<$ 0.1, ** p $<$ 0.05, *** p $<$ 0.01}\\
\end{tabular}}
\end{table}

>>>>

\caption{Hispanic identity and Skin Tone Implicit Bias Among Second Generation Hispanic Immigrants: By Parental Type\label{regtab-byparent-03}}
\centering
\resizebox{\linewidth}{!}{
\begin{tabular}[t]{lcccc}
\toprule
\multicolumn{1}{c}{ } & \multicolumn{1}{c}{All} & \multicolumn{1}{c}{HH} & \multicolumn{1}{c}{HW} & \multicolumn{1}{c}{WH} \\
\cmidrule(l{3pt}r{3pt}){2-2} \cmidrule(l{3pt}r{3pt}){3-3} \cmidrule(l{3pt}r{3pt}){4-4} \cmidrule(l{3pt}r{3pt}){5-5}
  & \specialcell{(1) \\ $H^2$} & \specialcell{(2) \\ $H^2$} & \specialcell{(3) \\ $H^2$} & \specialcell{(4) \\ $H^2$}\\
\midrule
Implicit Skin Tone Bias & \num{-0.04}* & \num{-0.04} & \num{-0.03} & \num{-0.05}\\
 & (\num{0.02}) & (\num{0.02}) & (\num{0.07}) & (\num{0.10})\\
Female & \num{0.00} & \num{-0.01} & \num{-0.01} & \num{0.02}\\
 & (\num{0.00}) & (\num{0.00}) & (\num{0.01}) & (\num{0.02})\\
College Graduate: Mother & \num{-0.05}*** & \num{-0.04}*** & \num{-0.04}*** & \num{-0.07}***\\
 & (\num{0.01}) & (\num{0.01}) & (\num{0.01}) & (\num{0.02})\\
College Graduate: Father & \num{-0.08}*** & \num{-0.04}*** & \num{-0.10}*** & \num{-0.11}***\\
 & (\num{0.01}) & (\num{0.01}) & (\num{0.02}) & (\num{0.02})\\
\midrule
N & \num{283872} & \num{210304} & \num{40957} & \num{32611}\\
Region FE & X & X & X & X\\
Year FE & X & X & X & X\\
Year-Region FE & X & X & X & X\\
\bottomrule
\multicolumn{5}{l}{\rule{0pt}{1em}\textsuperscript{1} I include controls for sex, quartic age, parental education.}\\
\multicolumn{5}{l}{\rule{0pt}{1em}\textsuperscript{2} Standard errors are clustered on the state level}\\
\multicolumn{5}{l}{\rule{0pt}{1em}* p $<$ 0.1, ** p $<$ 0.05, *** p $<$ 0.01}\\
\end{tabular}}
\end{table}

### 2023-09-02 my_paper/tables/tab17-iat_regression_tab_byparent_type_county.tex
first commit

\caption{Hispanic identity and Skin Tone Implicit Bias Among Second Generation Hispanic Immigrants: By Parental Type\label{regtab-byparent-03}}
\centering
\resizebox{\linewidth}{!}{
\begin{tabular}[t]{lcccc}
\toprule
\multicolumn{1}{c}{ } & \multicolumn{1}{c}{All} & \multicolumn{1}{c}{HH} & \multicolumn{1}{c}{HW} & \multicolumn{1}{c}{WH} \\
\cmidrule(l{3pt}r{3pt}){2-2} \cmidrule(l{3pt}r{3pt}){3-3} \cmidrule(l{3pt}r{3pt}){4-4} \cmidrule(l{3pt}r{3pt}){5-5}
  & \specialcell{(1) \\ $H^2$} & \specialcell{(2) \\ $H^2$} & \specialcell{(3) \\ $H^2$} & \specialcell{(4) \\ $H^2$}\\
\midrule
Implicit Skin Tone Bias & \num{-0.04}* & \num{-0.04} & \num{-0.03} & \num{-0.05}\\
 & (\num{0.02}) & (\num{0.02}) & (\num{0.07}) & (\num{0.10})\\
Female & \num{0.00} & \num{-0.01} & \num{-0.01} & \num{0.02}\\
 & (\num{0.00}) & (\num{0.00}) & (\num{0.01}) & (\num{0.02})\\
College Graduate: Mother & \num{-0.05}*** & \num{-0.04}*** & \num{-0.04}*** & \num{-0.07}***\\
 & (\num{0.01}) & (\num{0.01}) & (\num{0.01}) & (\num{0.02})\\
College Graduate: Father & \num{-0.08}*** & \num{-0.04}*** & \num{-0.10}*** & \num{-0.11}***\\
 & (\num{0.01}) & (\num{0.01}) & (\num{0.02}) & (\num{0.02})\\
\midrule
N & \num{283872} & \num{210304} & \num{40957} & \num{32611}\\
Region FE & X & X & X & X\\
Year FE & X & X & X & X\\
Year-Region FE & X & X & X & X\\
\bottomrule
\multicolumn{5}{l}{\rule{0pt}{1em}\textsuperscript{1} I include controls for sex, quartic age, parental education.}\\
\multicolumn{5}{l}{\rule{0pt}{1em}\textsuperscript{2} Standard errors are clustered on the state level}\\
\multicolumn{5}{l}{\rule{0pt}{1em}* p $<$ 0.1, ** p $<$ 0.05, *** p $<$ 0.01}\\
\end{tabular}}
\end{table}

>>>>

\caption{Hispanic identity and Skin Tone Implicit Bias Among Second Generation Hispanic Immigrants: By Parental Type (County)\label{regtab-byparent-03}}
\centering
\resizebox{\linewidth}{!}{
\begin{tabular}[t]{lcccc}
\toprule
\multicolumn{1}{c}{ } & \multicolumn{1}{c}{All} & \multicolumn{1}{c}{HH} & \multicolumn{1}{c}{HW} & \multicolumn{1}{c}{WH} \\
\cmidrule(l{3pt}r{3pt}){2-2} \cmidrule(l{3pt}r{3pt}){3-3} \cmidrule(l{3pt}r{3pt}){4-4} \cmidrule(l{3pt}r{3pt}){5-5}
  & \specialcell{(1) \\ $H^2$} & \specialcell{(2) \\ $H^2$} & \specialcell{(3) \\ $H^2$} & \specialcell{(4) \\ $H^2$}\\
\midrule
Implicit Skin Tone Bias & \num{0.00} & \num{0.01} & \num{-0.04} & \num{0.00}\\
 & (\num{0.01}) & (\num{0.02}) & (\num{0.04}) & (\num{0.03})\\
Female & \num{0.00} & \num{-0.01} & \num{0.00} & \num{0.02}\\
 & (\num{0.00}) & (\num{0.00}) & (\num{0.01}) & (\num{0.01})\\
College Graduate: Mother & \num{-0.05}*** & \num{-0.04}*** & \num{-0.05}*** & \num{-0.07}***\\
 & (\num{0.01}) & (\num{0.01}) & (\num{0.01}) & (\num{0.02})\\
College Graduate: Father & \num{-0.08}*** & \num{-0.04}*** & \num{-0.10}*** & \num{-0.12}***\\
 & (\num{0.01}) & (\num{0.01}) & (\num{0.02}) & (\num{0.02})\\
\midrule
N & \num{316554} & \num{232287} & \num{46428} & \num{37839}\\
Mean & \num{0.94} & \num{0.96} & \num{0.9} & \num{0.84}\\
Year-State FE & X & X & X & X\\
\bottomrule
\multicolumn{5}{l}{\rule{0pt}{1em}\textsuperscript{1} I include controls for sex, quartic age, parental education.}\\
\multicolumn{5}{l}{\rule{0pt}{1em}\textsuperscript{2} Standard errors are clustered on the state level}\\
\multicolumn{5}{l}{\rule{0pt}{1em}* p $<$ 0.1, ** p $<$ 0.05, *** p $<$ 0.01}\\
\end{tabular}}
\end{table}

### 2023-09-02 my_paper/tables/tab48-iat_regression_tab_bygrandparent_type-cg.tex
first commit

\begin{table}[!h]

\caption{Self-Reported Hispanic Identity and \citet{charlesPrejudiceWagesEmpirical2008} Prejudice  Measure: By Generation \label{regtab-bygen-cg}}
\centering
\resizebox{\linewidth}{!}{
\begin{threeparttable}
\begin{tabular}[t]{lcccc}
\toprule
  & \specialcell{(1) \\ All Gens \\ $H_{ist}$} & \specialcell{(2) \\  First Gen \\ $H^1_{ist}$} & \specialcell{(3) \\  Second Gen \\ $H^2_{ist}$} & \specialcell{(4) \\  Third Gen \\ $H^3_{ist}$}\\
\midrule
Bias & \num{-0.03} & \num{-0.02} & \num{-0.01} & \num{-0.13}**\\
 & (\num{0.03}) & (\num{0.02}) & (\num{0.02}) & (\num{0.06})\\
Female & \num{0.00} & \num{0.00} & \num{0.00} & \num{0.00}\\
 & (\num{0.00}) & (\num{0.00}) & (\num{0.00}) & (\num{0.00})\\
College Graduate: Mother & \num{-0.05}*** & \num{-0.04}*** & \num{-0.08}*** & \num{-0.07}***\\
 & (\num{0.01}) & (\num{0.01}) & (\num{0.01}) & (\num{0.01})\\
College Graduate: Father & \num{-0.07}*** & \num{-0.04}*** & \num{-0.10}*** & \num{-0.10}***\\
 & (\num{0.01}) & (\num{0.01}) & (\num{0.01}) & (\num{0.02})\\
\midrule
N & \num{906106} & \num{111960} & \num{605316} & \num{188830}\\
Mean & \num{0.89} & \num{0.96} & \num{0.92} & \num{0.76}\\
Year $\times$ Region FE & X & X & X & X\\
\bottomrule
\multicolumn{5}{l}{\rule{0pt}{1em}* p $<$ 0.1, ** p $<$ 0.05, *** p $<$ 0.01}\\
\end{tabular}
\begin{tablenotes}
\small
\item[1] \footnotesize{Each column is an estimation of equation (\ref{eq:identity_reg_bias}) by 
                      parents' type with region × year fixed effects with \citet{charlesPrejudiceWagesEmpirical2008} Prejudice  measure. 
                      \citet{charlesPrejudiceWagesEmpirical2008} use the General Security Survey of the most common racial questions between 1970-2000 for their measure of prejudice.
                      To use the prejudice   measure, I take the average of the GSS questions by year groups. The groups I use are as follows:
                      (1) 1977 and 1982, (2) 1985 and 1988, and 1989, (3) 1990, 1991, and 1993, and (4) 1994 and 1996. I link these groups to the following
                      grouped Current Population Survey (CPS) years: (1) 1994-1999, (2) 2000-2005, (3) 2006-2010, and (4) 2011-2016. 
                      In other words, I merge CPS data with the residual prejudice  measure from 20 years before the survey.
                      I include controls for sex, quartic age, parental education.
                      Standard errors are clustered on the state level.}
\item[2] \footnotesize{The samples include children ages 17 and below who live in intact families. 
                      First-generation Hispanic immigrant children that were born in a 
                      Spanish speaking county. Native born second-generation Hispanic 
                      immigrant children with at least one parent born in a Spanish speaking 
                      country. Finally, native born third-generation Hispanic immigrant children 
                      with native born parents and at least one grandparent born in a Spanish 
                      speaking country.}
\item[3] \footnotesize{Data source is the 2004-2021 Current Population Survey.}
\end{tablenotes}
\end{threeparttable}}
\end{table}

>>>>

\begin{table}[H]

\caption{Relationship Between Self-Reported Hispanic identity and \citet{charlesPrejudiceWagesEmpirical2008} Prejudice Measure Among Third-Generation Hispanic Immigrants: By Grandparentental Type \label{regtab-bygrandparent-cg}}
\centering
\resizebox{\linewidth}{!}{
\begin{threeparttable}
\begin{tabular}[t]{lcccc}
\toprule
\multicolumn{1}{c}{ } & \multicolumn{4}{c}{Numer of Hispanic Grandparents} \\
\cmidrule(l{3pt}r{3pt}){2-5}
  & \specialcell{(1) \\ One} & \specialcell{(2) \\ Two} & \specialcell{(3) \\ Three} & \specialcell{(4) \\ Four}\\
\midrule
Bias & \num{-0.14} & \num{-0.19}*** & \num{-0.13} & \num{-0.02}\\
 & (\num{0.10}) & (\num{0.07}) & (\num{0.19}) & (\num{0.03})\\
Female & \num{0.00} & \num{0.00} & \num{0.00} & \num{0.00}\\
 & (\num{0.01}) & (\num{0.01}) & (\num{0.01}) & (\num{0.00})\\
College Graduate: Mother & \num{-0.10}*** & \num{-0.08}*** & \num{0.02} & \num{-0.04}***\\
 & (\num{0.02}) & (\num{0.02}) & (\num{0.01}) & (\num{0.02})\\
College Graduate: Father & \num{-0.13}*** & \num{-0.09}*** & \num{0.00} & \num{-0.01}\\
 & (\num{0.03}) & (\num{0.02}) & (\num{0.02}) & (\num{0.02})\\
\midrule
N & \num{62969} & \num{68431} & \num{12111} & \num{45319}\\
Year $\times$ Region FE & X & X & X & X\\
\bottomrule
\multicolumn{5}{l}{\rule{0pt}{1em}* p $<$ 0.1, ** p $<$ 0.05, *** p $<$ 0.01}\\
\end{tabular}
\begin{tablenotes}
\small
\item[1] \footnotesize{Each column is an estimation of equation (\ref{eq:identity_reg_bias}) by 
                      grandparents' type with region × year fixed effects with \citet{charlesPrejudiceWagesEmpirical2008} prejudice measure. 
                      \citet{charlesPrejudiceWagesEmpirical2008} use the General Security Survey of the most common racial questions between 1970-2000 for their measure of prejudice.
                      To use the prejudice measure, I take the average of the GSS questions by year groups. The groups I use are as follows:
                      (1) 1977 and 1982, (2) 1985 and 1988, and 1989, (3) 1990, 1991, and 1993, and (4) 1994 and 1996. I link these groups to the following
                      grouped Current Population Survey (CPS) years: (1) 1994-1999, (2) 2000-2005, (3) 2006-2010, and (4) 2011-2016.
                      In other words, I merge CPS data with the residual prejudice measure from 20 years before the survey.
                      I include controls for sex, quartic age, parental education.
                      Standard errors are clustered on the state level.}
\item[2] \footnotesize{The samples include third-generation Hispanic children ages 17 and below who live in intact families. 
                      Native born third-generation Hispanic 
                      immigrant children with at least one grandparent born in a Spanish speaking 
                      country.}
\item[3] \footnotesize{Data source is the 2004-2021 Current Population Survey.}
\end{tablenotes}
\end{threeparttable}}
\end{table}

### 2023-09-02 my_paper/tables/tab52-iat_regression_tab_bygrandparent_type-cg-90s.tex
first commit

\begin{table}[!h]

\caption{Self-Reported Hispanic Identity and Charles and Guryan (2012) Prejeduice Measure: By Generation \label{regtab-bygen-cg-02}}
\centering
\resizebox{\linewidth}{!}{
\begin{threeparttable}
\begin{tabular}[t]{lcccc}
\toprule
  & \specialcell{(1) \\ All Gens \\ $H_i$} & \specialcell{(2) \\  First Gen \\ $H^1_i$} & \specialcell{(3) \\  Second Gen \\ $H^2_i$} & \specialcell{(4) \\  Third Gen \\ $H^3_i$}\\
\midrule
Bias & \num{-0.10}* & \num{-0.03} & \num{-0.09}* & \num{-0.26}**\\
 & (\num{0.05}) & (\num{0.02}) & (\num{0.05}) & (\num{0.12})\\
Female & \num{0.00} & \num{-0.01} & \num{0.01} & \num{-0.03}**\\
 & (\num{0.00}) & (\num{0.01}) & (\num{0.00}) & (\num{0.01})\\
College Graduate: Mother & \num{-0.10}*** & \num{-0.05}** & \num{-0.14}*** & \num{-0.12}***\\
 & (\num{0.02}) & (\num{0.02}) & (\num{0.02}) & (\num{0.03})\\
College Graduate: Father & \num{-0.13}*** & \num{-0.04} & \num{-0.17}*** & \num{-0.22}***\\
 & (\num{0.03}) & (\num{0.03}) & (\num{0.02}) & (\num{0.06})\\
\midrule
N & \num{157424} & \num{21888} & \num{105064} & \num{30472}\\
Mean & \num{0.83} & \num{0.96} & \num{0.87} & \num{0.58}\\
R squared & \num{0.384} & \num{0.018} & \num{0.223} & \num{0.249}\\
\bottomrule
\multicolumn{5}{l}{\rule{0pt}{1em}* p $<$ 0.1, ** p $<$ 0.05, *** p $<$ 0.01}\\
\end{tabular}
\begin{tablenotes}
\small
\item[1] \footnotesize{Each column is an estimation of equation (\ref{eq:identity_reg_bias}) by 
                      parents' type with Charles and Guryan (2012) Prejeduice measure. 
                      Charles and Guryan (2012) use the General Security Survey of the most common racial questions between 1970-2000 for their measure of prejeduice.
                      To use Charles and Guryan (2012) prejeduice measure, I merge the GSS index in 1996 with CPS 1995-1999 years. 
                      In other words, I merge CPS data with the residual prejeduice measure from 20 years before the survey.
                      I include controls for sex, quartic age, parental education.
                      Standard errors are clustered on the state level}
\item[2] \footnotesize{The samples include children ages 17 and below who live in intact families. 
                      First-generation Hispanic immigrant children that were born in a 
                      Spanish speaking county. Native born second-generation Hispanic 
                      immigrant children with at least one parent born in a Spanish speaking 
                      country. Finally, native born third generation Hispanic immigrant children 
                      with native born parents and at least one grand parent born in a Spanish 
                      speaking country.}
\item[3] \footnotesize{Data source is the 2004-2020 Current Population Survey.}
\end{tablenotes}
\end{threeparttable}}
\end{table}

>>>>

\begin{table}[H]

\caption{Self-Reported Hispanic identity and Charles and Guryan (2012) Prejeduice Measure Among Third Generation Hispanic Immigrants: By Grandparents Type (State) \label{regtab-bygrandparent-cg-02}}
\centering
\resizebox{\linewidth}{!}{
\begin{threeparttable}
\begin{tabular}[t]{lcccc}
\toprule
\multicolumn{1}{c}{ } & \multicolumn{4}{c}{Numer of Hispanic Grandparents} \\
\cmidrule(l{3pt}r{3pt}){2-5}
  & \specialcell{(1) \\ One} & \specialcell{(2) \\ Two} & \specialcell{(3) \\ Three} & \specialcell{(4) \\ Four}\\
\midrule
Bias & \num{-0.22}* & \num{-0.34}** & \num{-0.57}** & \num{0.16}\\
 & (\num{0.11}) & (\num{0.13}) & (\num{0.21}) & (\num{0.10})\\
Female & \num{-0.04}*** & \num{-0.05}** & \num{0.04} & \num{0.00}\\
 & (\num{0.01}) & (\num{0.02}) & (\num{0.04}) & (\num{0.02})\\
College Graduate: Mother & \num{-0.10}** & \num{-0.10} & \num{-0.04} & \num{-0.19}***\\
 & (\num{0.04}) & (\num{0.07}) & (\num{0.23}) & (\num{0.06})\\
College Graduate: Father & \num{-0.14}*** & \num{-0.15}*** & \num{-0.08} & \num{-0.06}\\
 & (\num{0.02}) & (\num{0.04}) & (\num{0.16}) & (\num{0.08})\\
\midrule
N & \num{14931} & \num{10126} & \num{1848} & \num{3567}\\
Year $\times$ Region FE & X & X & X & X\\
\bottomrule
\multicolumn{5}{l}{\rule{0pt}{1em}* p $<$ 0.1, ** p $<$ 0.05, *** p $<$ 0.01}\\
\end{tabular}
\begin{tablenotes}
\small
\item[1] \footnotesize{Each column is an estimation of equation (\ref{eq:identity_reg_bias}) by 
                      parents' type with Charles and Guryan (2012) Prejeduice measure. 
                      Charles and Guryan (2012) use the General Security Survey of the most common racial questions between 1970-2000 for their measure of prejeduice.
                      To use Charles and Guryan (2012) prejeduice measure, I merge the GSS index in 1996 with CPS 1995-1999 years. 
                      In other words, I merge CPS data with the residual prejeduice measure from 20 years before the survey.
                      I include controls for sex, quartic age, parental education.
                      Standard errors are clustered on the state level}
\item[2] \footnotesize{The samples include third-generation Hispanic children ages 17 and below who live in intact families. 
                      Native born Third-generation Hispanic 
                      immigrant children with at least one grandparent born in a Spanish speaking 
                      country.}
\item[3] \footnotesize{Data source is the 2004-2020 Current Population Survey.}
\end{tablenotes}
\end{threeparttable}}
\end{table}
